Simulating High-Dimensional Multivariate Data

### 2021-02-27 020-simulation-algorithm.Rmd
fixed italic bug

    (i$^\prime$) Convert the target Kendall $\tau$ matrix $R_K$ to the corresponding MVN Pearson correlation $R_X$.
2. Check admissibility and, if needed, compute the nearest correlation matrix.
    (i) Check that $R_X$ is a correlation matrix, a positive definite matrix with 1's along the diagonal.   
	(ii) If $R_X$ is a correlation matrix, the input matrix is *admissible* in this scheme.
	Otherwise,
    (ii$^\prime$) Replace $R_X$ with the nearest correlation matrix $\tilde{R}_X$, in the Frobenius norm.
3. NORTA step
    (i) Generate ${\bf X}=(X_1, \ldots, X_d) \sim N_d({\bf 0}, R_X)$.  
    (ii) Transform ${\bf X}$ to ${\bf U} = (U_1, \ldots,  U_d)$ viz $U_i=\Phi(X_i)$, $i=1, \ldots, d$.  
    (iii) Return ${\bf Y}  = (Y_1, \ldots,  Y_d)$, where $Y_i=F_i^{-1}(U_i)$, $i=1, \ldots, d$.

@@

*Pearson Matching*
Given a desired target correlation $\rho_Y$ between a pair of marginal distributions, the correlation coefficient $\rho_Z$ used in the Gaussian copula must be specified so as to satisfy equation \@ref(eq:pearsonIntegralRelation).

@@

This algorithm is trying to find a correlation matrix $X$ close to $G$ in the convex optimization problem:

@@

* Qi, H., & Sun, D. (2006). A quadratically convergent Newton method for computing the nearest correlation matrix. SIAM journal on matrix analysis and applications, 28(2), 360-385.

>>>>

    (i') Convert the target Kendall $\tau$ matrix $R_K$ to the corresponding MVN Pearson correlation $R_X$.
2. Check admissibility and, if needed, compute the nearest correlation matrix.
    (i) Check that $R_X$ is a correlation matrix, a positive definite matrix with 1's along the diagonal.   
	(ii) If $R_X$ is a correlation matrix, the input matrix is *admissible* in this scheme.
	Otherwise,
    (ii$^\prime$) Replace $R_X$ with the nearest correlation matrix $\tilde{R}_X$, in the Frobenius norm.
3. NORTA step
    (i) Generate ${\bf X}=(X_1, \ldots, X_d) \sim N_d({\bf 0}, R_X)$.  
    (ii) Transform ${\bf X}$ to ${\bf U} = (U_1, \ldots,  U_d)$ viz $U_i=\Phi(X_i)$, $i=1, \ldots, d$.
    (iii) Return ${\bf Y}  = (Y_1, \ldots,  Y_d)$, where $Y_i=F_i^{-1}(U_i)$, $i=1, \ldots, d$.

@@

*Pearson Matching*

Given a desired target correlation $\rho_Y$ between a pair of marginal distributions, the correlation coefficient $\rho_Z$ used in the Gaussian copula must be specified so as to satisfy equation \@ref(eq:pearsonIntegralRelation).

@@

Finding the nearest correlation matrix to an *almost* correlation matrix is a problem that has been researched since the 1990's, and improved upon in the 2000's by Nick Higham who presented an alternating projection algorithm (@higham2002computing) which is used by R (`Matrix::nearPD`), and then by Qi and Sun who developed a quadratically convergent algorithm based on the theory of strongly semismooth matrix functions (@qi2006quadratically). Our algorithm is transcription of the `R` code shared by Sun to the Julia language. The nearest correlation matrix problem can be written down as the following convex optimization problem:

@@
